---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# app91

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

As a part of the [The 1991 Project](https://the1991project.com/) of the [Mercatus Center](https://www.mercatus.org/) at the [George Mason Univeristy](https://www.gmu.edu/), this app aims to provide intuition about movements in economic growth. 

## NOTICE

Currently this is a project under development. The application is a work in progress. It is not yet publicly released. The app has not yet found its permanent home, remains to be hosted to a permanent url for general use.


## Installation

You can install the development version of app91 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AyushBipinPatel/app91")
```

## Example

This package is a [golem](https://golemverse.org/) framework of a [Shiny](https://shiny.rstudio.com/) application. Therefore, this Shiny application can be installed as a package on your machine by following the steps.

```{r example, eval=FALSE}
library(app91)

app91::run_app()

```



## Code of Conduct
  
Please note that the app91 project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
